Arrows for Parallel Computations

### 2017-12-12 paper/content/parrows.tex
minor

\subsubsection{Glasgow parallel Haskell} \label{sec:parrows:multicore}
The GpH implementation of |ArrowParallel| is implemented in a straightforward manner, but a bit different to the variant from Section \ref{sec:GpHIntro} by using |evalN :: [arr a b] -> arr [a] [b]| (think |zipWith ($) fs as| on Arrows, definition in Appendix~\ref{utilfns}) combined with |withStrategy :: Strategy a -> a -> a| from GpH, where |withStrategy| is the same as |using :: a -> Strategy a -> a|, but with flipped parameters. Our |Conf a| datatype simply wraps a |Strategy a|, but could be extended in future versions of our DSL.
\begin{figure}[t]
\begin{code}
data Conf a = Conf (Strategy a)

>>>>

\subsubsection{Glasgow parallel Haskell} \label{sec:parrows:multicore}
The GpH implementation of |ArrowParallel| is implemented in a straightforward manner, but a bit different compared to the variant from Section \ref{sec:GpHIntro}, by using |evalN :: [arr a b] -> arr [a] [b]| (think |zipWith ($) fs as| on Arrows, definition in Appendix~\ref{utilfns}) combined with |withStrategy :: Strategy a -> a -> a| from GpH, where |withStrategy| is the same as |using :: a -> Strategy a -> a|, but with flipped parameters. Our |Conf a| datatype simply wraps a |Strategy a|, but could be extended in future versions of our DSL.
\begin{figure}[t]
\begin{code}
data Conf a = Conf (Strategy a)
